---
title: "BAE 204 - Lab #12: Calculate nitrate removal kinetics in a wetland : Report"
author: "your name"
date: "4/8/2021"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.height=5, fig.width=9, fig.align="center", echo = FALSE)
```

# Exercise 1: Explore the content of the data and first plot

I was given a first file ("infreq_Exp06_Rep2_U0.csv") of nitrate concentration decrease over time in a mesocosm experiment. First I plotted the nitrate concentration decrease as a function of time expressed in days. 

```{r, echo=TRUE, eval=TRUE}
data<-read.csv(file="https://raw.githubusercontent.com/francoisbirgand/BAE204-removal_kinetics_lab/master/infreq_Exp06_Rep2_U0.csv",header = TRUE) #Reads file into table format
timeday <- data$time/24/3600
conc <- data$conc
xlimtime <- range(timeday)
ylimconc <- range(conc)
plot(timeday,conc,
     xlim = xlimtime, ylim = ylimconc,
     xlab = "time in days", ylab = "nitrate concentrations (mg N/L)",
     main = "title")
######## Add below 
```

</br></br>

# Exercise 2 : Fitting a first order rate model for nitrate removal in a wetland

\[
C(t)=C_0e^{-\frac{\rho}{D}(t-t_0)}
\]

\[
\frac{C(t)}{C_0}=e^{-\frac{\rho}{D}(t-t_0)}
\]

\[
\ln{\frac{C(t)}{C_0}}=-\frac{\rho}{D}(t-t_0)
\]

</br></br>

# Exercise 3 : Fitting a first order rate model by calculating mass transfer coefficient   

```{r, echo=TRUE, eval=TRUE}
x <- timeday - timeday[1]
y <- log(conc/conc[1])
plot(x,y)
linreg <- lm(y~x+0)
abline(linreg)
slope <- linreg$coefficients
rho <- -slope*0.1
signif(rho,2)

######## Add below 
```
</br></br>

The value that I calculated is `r signif(rho,2)` proper unit.


# Exercice 4: Treatment time for stagnant water


</br></br>

# Exercise 5: Treatment time for water recirculated at 3 cm/s

```{r, echo=TRUE, eval=TRUE}
data2<-read.csv(file="https://raw.githubusercontent.com/francoisbirgand/BAE204-removal_kinetics_lab/master/Exp03_Rep3_U3.csv",header = TRUE) #Reads file into table format

```

</br></br>

## Exercise 6: Discuss your observations 