---
title: "BAE 204 - Lab #12: Calculate nitrate removal kinetics in a wetland : Report"
author: "your name"
date: "4/2/2020"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.height=5, fig.width=9, fig.align="center", echo = FALSE)
```

# Exercise 1: Explore the content of the data and first plot

I was given a first file ("infreq_Exp06_Rep2_U0.csv") of nitrate concentration decrease over time in a mesocosm experiment. First I plotted the nitrate concentration decrease as a function of time expressed in days. 

```{r, echo=TRUE, eval=TRUE}
data<-read.csv(file="https://raw.githubusercontent.com/francoisbirgand/BAE204-removal_kinetics_lab/master/infreq_Exp06_Rep2_U0.csv",header = TRUE) #Reads file into table format

######## Add below 
```

</br></br>

# Exercise 2 : Fitting a first order rate model for nitrate removal in a wetland


</br></br>

# Exercise 3 : Fitting a first order rate model by calculating mass transfer coefficient   


</br></br>

# Exercice 4: Treatment time for stagnant water


</br></br>

# Exercise 5: Treatment time for water recirculated at 3 cm/s

```{r, echo=TRUE, eval=TRUE}
data2<-read.csv(file="https://raw.githubusercontent.com/francoisbirgand/BAE204-removal_kinetics_lab/master/Exp03_Rep3_U3.csv",header = TRUE) #Reads file into table format

```

</br></br>

## Exercise 6: Discuss your observations 